---
title: "BiomassSpeciesData"
author: "Eliot McIntire, Alex M Chubaty, Cerer Barros"
date: "16 July 2018"
output:
  pdf_document: default
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

# Overview

Download and pre-process proprietary LandWeb data (CASFRI + Paul Pickell's dataset) and kNN species biomass data
Full data only available to authorized Google users.
Defaults to extracting 5 species/genera Abies sp., Picea glauca, Picea mariana, Pinus sp. and  Populus tremuloides.

# Links to other modules

Intended for use with the Land-R-Biomass* suite of models - if LandWeb project permissions are valid, then the full datasets used for the LandWeb can be used here.

```{r}
## as of Nov 25th 2019
devtools::install_github("PredictiveEcology/reproducible@development", dependencies = FALSE)
devtools::install_github("PredictiveEcology/SpaDES.core@development", dependencies = FALSE)
devtools::install_github("PredictiveEcology/pemisc@development") ## TODO: use LandR

library(magrittr)
library(raster)
library(SpaDES)
library(pemisc) ## TODO: use LandR

options(reproducible.inputPaths = "E:/Data/LandR_related/")
setPaths(modulePath = "../", cachePath = "cache/")

## do you want to hand-draw a map or use defaults?
# - note that large areas will take longer to compute
handDrawMap <- FALSE

if(handDrawMap) {
  dev()
  clearPlot()
  canadaMap <- Cache(getData, 'GADM', country = 'CAN', level = 1, path = "data/",
                     cacheRepo = getPaths()$cachePath, quick = FALSE)
  LIM_SA <- shapefile("../LandscapesInMotion/data/maps/Foothills_study_area.shp")
  Plot(canadaMap, speedup = 5, visualSqueeze = 0.9) # 5 seemed optimal
  Plot(LIM_SA, addTo = "canadaMap", col = "green")
  
  ## hand-drawn study area
  if(!exists("studyAreaLarge")) {
    message("Since there is no object called 'studyAreaLarge', please draw a study area with 10 points")
    severalrandompoints <- clickCoordinates(10)
    if(startsWith(attr(severalrandompoints, "tags"), "cache")) message("Taking studyAreaLarge from Cache")
    studyAreaLarge <- SpatialPolygons(list(Polygons(list(Polygon(severalrandompoints$coords)), ID = "handDrawnPoly")),
                                          proj4string = crs(canadaMap))
  }
}

modules <-  list("BiomassSpeciesData")
objects <- if(handDrawMap) {
  list("studyAreaLarge" = studyAreaLarge,
       "studyArea" = studyAreaLarge)  
} else list()

opts <- options(reproducible.useCache = FALSE)
mySim <- simInit(modules = modules, objects = objects)

mySimOut <- spades(mySim)
options(opts)
```

